---
title: "honor thesis"
output:
  html_document: default
  pdf_document:
    latex_engine: xelatex
date: "2023-03-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tseries)
library(vars)
library(tidyverse)
library(forecast)
library(urca)
library(lmtest)

# Define a function to calculate RMSE for different filter sizes
smooth_RMSE <- function(data, filter_sizes) {
  rmse <- numeric(length(filter_sizes))
  for (i in 1:length(filter_sizes)) {
    smooth_data <- stats::filter(data, pascal_filter(filter_sizes[i]), sides = 2)
    rmse[i] <- accuracy(smooth_data, data)[2]
  }
  return(rmse)
}

pascal_filter <- function(n) {
  pascal_row <- c(1)
  for (i in 1:(n - 1)) {
    pascal_row <- c(0, pascal_row) + c(pascal_row, 0)
  }
  return(pascal_row / sum(pascal_row))
}

# Load data and create time series
data <- read_xlsx("50kk_quarterly_thesis_data.xlsx")
data$year <- as.Date(paste0(data$year, "-01-01"))

CO2_emission_ts <- ts(data$co2, start = c(1990, 1), end = c(2020, 4), frequency = 4)
green_patent_index_ts <- ts(data$sum_patentindex, start = c(1990, 1), end = c(2020, 4), frequency = 4)
gdp_per_ts <- ts(data$gdp_per, start = c(1990, 1), end = c(2020, 4), frequency = 4)
energy_price_ts <- ts(data$energy_price, start = c(1990, 1), end = c(2020, 4), frequency = 4)

# Define a range of filter sizes to test
filter_sizes <- 1:10

# Calculate RMSE for different filter sizes for each time series
rmse_CO2 <- smooth_RMSE(CO2_emission_ts, filter_sizes)
rmse_green <- smooth_RMSE(green_patent_index_ts, filter_sizes)
rmse_gdp_per <- smooth_RMSE(gdp_per_ts, filter_sizes)
rmse_energy_price <- smooth_RMSE(energy_price_ts, filter_sizes)

# Plot RMSE vs. filter size for each time series
par(mfrow = c(2, 2))
plot(filter_sizes, rmse_CO2, type = "l", xlab = "Filter Size", ylab = "RMSE", main = "CO2_emission_ts")
plot(filter_sizes, rmse_green, type = "l", xlab = "Filter Size", ylab = "RMSE", main = "green_patent_index_ts")
plot(filter_sizes, rmse_gdp_per, type = "l", xlab = "Filter Size", ylab = "RMSE", main = "gdp_per_ts")
plot(filter_sizes, rmse_energy_price, type = "l", xlab = "Filter Size", ylab = "RMSE", main = "energy_price_ts")


# Identify optimal filter size with the minimum RMSE for each time series
optimal_size_CO2 <- filter_sizes[which.min(rmse_CO2)]
cat("Optimal filter size for CO2_emission_ts:", optimal_size_CO2, "\n")

optimal_size_green <- filter_sizes[which.min(rmse_green)]
cat("Optimal filter size for green_patent_index_ts:", optimal_size_green, "\n")

optimal_size_gdp_per <- filter_sizes[which.min(rmse_gdp_per)]
cat("Optimal filter size for gdp_per_ts:", optimal_size_gdp_per, "\n")

optimal_size_energy_price <- filter_sizes[which.min(rmse_energy_price)]
cat("Optimal filter size for energy_price_ts:", optimal_size_energy_price, "\n")


```

```{r}
library(tseries)
library(vars)
library(tidyverse)
library(forecast)
library(urca)
library(lmtest)


# Load data and create time series
data <- read_xlsx("50kk_quarterly_thesis_data.xlsx")
data$year <- as.Date(paste0(data$year, "-01-01"))

CO2_emission_ts <- ts(data$co2, start = c(1990, 1), end = c(2020, 4), frequency = 4)
green_patent_index_ts <- ts(data$sum_patentindex, start = c(1990, 1), end = c(2020, 4), frequency = 4)
gdp_per_ts <- ts(data$gdp_per, start = c(1990, 1), end = c(2020, 4), frequency = 4)
energy_price_ts <- ts(data$energy_price, start = c(1990, 1), end = c(2020, 4), frequency = 4)

# Step 1: Data visualization
autoplot(cbind(CO2_emission_ts, green_patent_index_ts, gdp_per_ts, energy_price_ts), facet = TRUE) +
  labs(title = "Time Series Plots",
       x = "Time",
       y = "Values",
       color = "Variables")

# pascal filter to selected variables
# Create Pascal filters of size 9 and size 7
pascal_filter_9 <- pascal_filter(9)

# Apply Pascal filters to gdp_per and industry_production
smoothed_gdp_per_ts <- stats::filter(gdp_per_ts, pascal_filter_9, sides = 2)

# View the smoothed time series
autoplot(cbind(gdp_per_ts), facet = TRUE) +
  labs(title = "Smoothed Time Series",
       x = "Time",
       y = "Values",
       color = "Variables")
# trim data after smooth
# Remove the first 4 observations from each time series
CO2_emission_ts <- window(CO2_emission_ts,  start = c(1991, 1), end = c(2019, 4))
green_patent_index_ts <- window(green_patent_index_ts,  start = c(1991, 1), end = c(2019, 4))
gdp_per_ts <- window(smoothed_gdp_per_ts,  start = c(1991, 1), end = c(2019, 4))
energy_price_ts <- window(energy_price_ts,  start = c(1991, 1), end = c(2019, 4))

# Step 2: Stationarity test (Augmented Dickey-Fuller test) before log transformation
all_data <- cbind(CO2_emission_ts, green_patent_index_ts, gdp_per_ts, energy_price_ts)
adf_results_before_log <- lapply(as.data.frame(all_data), adf.test)
p_values <- sapply(adf_results_before_log, function(x) x$p.value)
names(p_values) <- colnames(all_data)
p_values


# Apply log transformation to the rest of the variables
log_green_patent_index_ts <- log(green_patent_index_ts)
log_gdp_per_ts <- log(gdp_per_ts)
log_energy_price_ts <- log(energy_price_ts)

# Combine CO2_emission_ts with the log-transformed variables
# Apply first differencing to the log-transformed variables except CO2_emission_ts
d_log_green_patent_index_ts <- diff(log_green_patent_index_ts)
d_log_gdp_per_ts <- diff(log_gdp_per_ts)
d_log_energy_price_ts <- diff(log_energy_price_ts)

# Combine the CO2_emission_ts and the differenced variables
combined_data_diff <- cbind(CO2_emission_ts[-1], d_log_green_patent_index_ts, d_log_gdp_per_ts, d_log_energy_price_ts)

# Estimate the VAR model with the appropriate lag length
lag_selection <- VARselect(combined_data_diff, lag.max = 4, type = "both")
selected_lag <- lag_selection$selection[1]
VAR_model <- VAR(combined_data_diff, p = selected_lag)
summary(VAR_model)


# Step 6: Impulse Response Function
irf_results <- irf(VAR_model, n.ahead = 4)
plot(irf_results)

# Step 7: Cointegration test (Johansen test)
coint_test <- ca.jo(combined_data_diff, type = "eigen", ecdet = "trend", K = 2)
summary(coint_test)

# Step 8: Granger Causality Test
# Perform Granger causality tests using the estimated VAR model
granger_test_CO2 <- causality(VAR_model, cause = "CO2_emission_ts..1.")
granger_test_patent <- causality(VAR_model, cause = "d_log_green_patent_index_ts")
granger_test_gdp_per <- causality(VAR_model, cause = "d_log_gdp_per_ts")
granger_test_energy_price <- causality(VAR_model, cause = "d_log_energy_price_ts")

print(granger_test_CO2)
print(granger_test_patent)
print(granger_test_gdp_per)
print(granger_test_energy_price)

```

```{r}
# Combine the variables in the desired order
combined_data_diff <- cbind(d_log_energy_price_ts, d_log_green_patent_index_ts, d_log_gdp_per_ts, CO2_emission_ts[-1])

# Estimate the VAR model with the appropriate lag length
lag_selection <- VARselect(combined_data_diff, lag.max = 4, type = "both")
selected_lag <- lag_selection$selection[1]
VAR_model <- VAR(combined_data_diff, p = selected_lag)
summary(VAR_model)

# Step 6: Impulse Response Function
irf_results <- irf(VAR_model, n.ahead = 4)
plot(irf_results)

# Step 7: Cointegration test (Johansen test)
coint_test <- ca.jo(combined_data_diff, type = "eigen", ecdet = "trend", K = 2)
summary(coint_test)



```




```{r}
# Load required packages
library(readxl)
library(forecast)
library(vars)
library(urca)
library(ggplot2)
library(tseries)
library(tsDyn)

# (Your data loading and preprocessing code remains unchanged)

# Estimate the cointegrating relations using the ca.jo function
coint_test <- ca.jo(combined_data_diff, type = "eigen", ecdet = "trend", K = 2)

# Fit the VECM model using the VECM function from tsDyn package
VECM_model <- VECM(combined_data_diff, r = 3, lag = 1, estim = "ML", LRinclude = "const") # Use r = 4 since r<=4 is significant

# Obtain the residuals of the VECM model
resid_VECM <- residuals(VECM_model)

# Estimate the optimal lag for the residual-based VAR model
lag_selection_resid <- VARselect(resid_VECM, lag.max = 4, type = "both")
selected_lag_resid <- lag_selection_resid$selection[1]

# Fit a residual-based VAR model
VAR_resid_model <- VAR(resid_VECM, p = selected_lag_resid)
summary(VAR_resid_model)

# Impulse Response Function
irf_results_VECM <- irf(VAR_resid_model, n.ahead = 4)
plot(irf_results_VECM)

# Granger Causality Test
granger_test_CO2 <- causality(VAR_resid_model, cause = "CO2_emission_ts..1.")
granger_test_patent <- causality(VAR_resid_model, cause = "d_log_green_patent_index_ts")
granger_test_gdp_per <- causality(VAR_resid_model, cause = "d_log_gdp_per_ts")
granger_test_energy_price <- causality(VAR_resid_model, cause = "d_log_energy_price_ts")

print(granger_test_CO2)
print(granger_test_patent)
print(granger_test_gdp_per)
print(granger_test_energy_price)

```


##When use the irf() function with the ortho = TRUE option in R, it automatically calculates the orthogonalized impulse response function based on the Cholesky decomposition of the error variance-covariance matrix, taking into account the ordering of the variables.
The ordering of the variables is crucial because it determines the contemporaneous relationships between the variables in the model:

The first variable in the ordering is assumed to contemporaneously affect all other variables.
The second variable is assumed to contemporaneously affect all other variables except the first one.
The process continues in a similar manner for the rest of the variables in the ordering.

the impulse variable is d_green_patent_index_ts, which means I want to understand the effect of a shock to d_green_patent_index_ts on the response variables d_CO2_emission_ts and d_gdp_per_ts. The orthogonalized impulse response functions will account for the contemporaneous correlations between the shocks when calculating the response of d_CO2_emission_ts and d_gdp_per_ts to the shock in d_green_patent_index_ts.

The coefficients of the lagged variables show the effect of each variable on the other variables in the model. For example, if the coefficient of the lagged green_patent_index variable on the CO2_emission variable is negative, then we can conclude that an increase in green patents is associated with a decrease in CO2 emissions.

The variance-covariance matrix shows the covariance between each variable in the model. A positive covariance between two variables indicates that they tend to move together over time, while a negative covariance indicates that they tend to move in opposite directions.

The impulse response functions show the response of each variable to a one-unit shock in each of the other variables. For example, if the impulse response function for the CO2_emission variable in response to a shock in the green_patent_index variable is negative, then we can conclude that an increase in green patents leads to a decrease in CO2 emissions.


since the p-value is smaller than the significance level of 0.05 (assuming a 95% confidence level), we fail to reject the null hypothesis. This means the variables are not cointegrated. I will proceed with a first-difference VAR model. By differencing the data, I transform the non-stationary variables into stationary ones, avoiding the problem of spurious regressions.


The Granger Causality test of the whole model is significant. When I use lag=1, the result is insignificant, when I use lag=3 based on Akaike Information Criterion, the result is significant. However, green patent index itself does not granger cause CO2_emission no matter which lag value I choose.
```{r}
```